---
title: "Geniole et al 2019"
author: Lincoln J Colling
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: FALSE
    citation_package: biblatex
documentclass: "article"
biblio-style: "apa"
classoption: ["a4paper","12pt"]
bibliography: ['references.bib','geniole.bib']

header-includes:
  - \usepackage{pdflscape}
  - \usepackage{makecell}
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
xfun::pkg_attach2("tidyverse",
"knitr",
"kableExtra",
"rmarkdown",
"bookdown",
"bib2df")

remotes::install_github("ljcolling/ODPHelper")
options(kableExtra.latex.load_packages = TRUE)
geniole <- readRDS("../made/geniole.Rdata")
geniole_download <- readRDS("../made/geniole_download_info.Rdata")
readr::write_lines(unlist(geniole$session_info$citations), path = "geniole.bib")
library(ODPHelper)
as_tibble <- as_data_frame
keys = keys_from_session(geniole$session_info$citations)
keys <- keys[!(keys %in% "R-ODPHelper")]
```

\newpage

# Introduction

This documents contains the reanalysis of the following paper:

Geniole, S. N., Procyshyn, T. L., Marley, N., Ortiz, T. L., Bird, B. M., Marcellus, A. L., … Carré, J. M. (2019). Using a Psychopharmacogenetic Approach To Identify the Pathways Through Which—and the People for Whom—Testosterone Promotes Aggression. *Psychological Science, 30*(4), 481–494. 

@Geniole provided a mix of R code and SPSS code for their analyses. However, all re-analyses were performed in R. Wherever possible their original R code was used as the starting point for the re-analysis.

The analysis code is available at [https://github.com/ljcolling/odp-geniole](https://github.com/ljcolling/odp-geniole). This document is automatically built. To manually build this document, clone the git repository and run `make all`.

## Data download

A total of `r length(geniole_download$files)` files were downloaded from [`r glue::glue("https://osf.io/{geniole_download$node}")`](`r glue::glue("https://osf.io/{geniole_download$node}")`). The downloaded files the MD5 hashes are shown in Table \@ref(tab:genioletable1).

```{r genioletable1, echo=FALSE}
tibble::tibble(`File name` = stringr::str_remove_all(names(geniole_download$hashes),"./data/"), `MD5 Hash` = geniole_download$hashes) %>%  knitr::kable(digits = 3, booktabs = T, caption = "Files downloaded for Geniole et al. (2019)", escape = T, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") 
```

# Drug administration

For the Drug $\times$ Time interaction we were able to reproduce the results reported in @Geniole (`r geniole$drug_val_anova`). For the paired *t*-test we were similarly able to reproduce the results (`r geniole$drug_val_ttests`). However, we were not able to reproduce the reported Cohen's *d* values because the standardiser (i.e., how the standard deviation was pooled) was not reported. 

# Archival data set

For the archival data set we were largely able reproduce the results in Table 2 [@Geniole] expect for the effect size measures. The differences in the effect size measures were typically small, and are likely due to rounding differences. However, there was a more serious difference on row 4 of the table where the Cohen's *d* reported by @Geniole appears to have it's sign reversed. Our re-analysis produced a Cohen's *d* with the correct sign. Because of this sign error in the reporting by @Geniole, there is also a difference in corresponding confidence interval. Our reproduction of Table 2 [@Geniole] is shown in Table \@ref(tab:genioletable2).

```{r genioletable2, echo=FALSE}
labels_recode = c("std(riskc)" = "Personality-risk score", 
  "center(drugcond)" = "Drug group", 
  "std(riskc):center(drugcond)" = "Drug group $\\times$ Personality-risk score", 
"center(drugcond)" = "Drug group's conditional effect at\nlow personality-risk score", 
"center(drugcond)" = "Drug group's conditional effect at\nhigh personality-risk score") 
geniole$table2 %>% mutate(`Analysis and predictor of agression` = labels_recode) %>% 
  mutate_all(linebreak) %>%
  knitr::kable(digits = 3, booktabs = T, caption = "Reproduction of Table 2 (Geniole et al., 2019)", escape = F, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  pack_rows(group_label = "Analysis A", start_row = 1, end_row = 3) %>%
  pack_rows(group_label = "Analysis B", start_row = 4, end_row = 5) #%>% landscape()
```

# Current data set

Again we were largely able to reproduce the results in Table 3 [@Geniole] except for the effect size measures. The differences in the effect size measures again slight, and is likely due to rounding differences. Our reproduction of Table 3 [@Geniole] is shown in Table \@ref(tab:genioletable3).


Our re-analysis was also able to reproduce the results presented in Table 4 of @Geniole but again with small differences in the effect sizes measures. Our reproduction of Table 4 is shown in \@ref(tab:genioletable4)


Our re-analysis was able to reproduce the results presented in Table 5 of @Geniole again with slight differences in the effect measures and a small difference in the final *b* value. Again, these are likely to reflect rounding errors. 

@Geniole also report a number of results in the text of the section titled *Are testosterone’s effects at high personality risk and low CAG repeat length explained, in part, by variation in feelings of reward or anger?*. Again, we were largely able to reproduce these expect for small different that are likely to reflect rounding errors. The orginal results and the reproduced results are listed below.

**Original**

1. *n* = 224, *b* = 0.889, *SE* = 0.361, *t*(216) = 2.463, *p* = .015, *r* = .165, Cohen’s *d* = 0.335, 95% CI = [0.065, 0.605].

2. *n* = 306, *b* = 0.207, *SE* = 0.362, *t*(298) = 0.572, *p* = .568, *r* = .033, Cohen’s *d* = 0.066, 95%CI = [−0.162, 0.294]

3. *n* = 224, *b* = 7.960, *SE* = 2.201, *t*(216) = 3.617, *p* < .001, *r* = .239, Cohen’s *d* = 0.492, 95% CI = [0.220, 0.764]

4. *b* = 3.940, *SE* = 2.396, *t*(212) = 1.644, *p* = .102, *r* = .112, Cohen’s *d* = 0.226, 95% CI = [−0.046, 0.498]

5. *n* = 224, *b* = 4.031, *SE* = 0.946, *t*(212) = 4.260, *p* < .001, *r* = .281, Cohen’s *d* = 0.585, 95% CI = [0.308, 0.862]

**Reproduced**

1. `r geniole$intext_stats[[1]]`

2. `r geniole$intext_stats[[2]]`

3. `r geniole$intext_stats[[3]]`

4. `r geniole$intext_stats[[4]]`

5. `r geniole$intext_stats[[5]]`

# `R` information {-}

We performed our analysis on `r geniole$session_info$sessionInfo$R.version$version.string` with all packages installed from a timestamped version of MRAN (date: `r str_remove(geniole$session_info$cran,"https://mran.microsoft.com/snapshot/")`). The following R packages were used: `r paste0(map_chr(keys, function(x) glue::glue("@{x}")), collapse = ", ")`.


```{r genioletable3, echo=FALSE}
labels_recode = c("std(riskc)" = "Personality-risk score", 
  "center(drugcond)" = "Drug group", 
  "std(riskc):center(drugcond)" = "Drug group $\\times$ Personality-risk score", 
"center(drugcond)" = "Drug group's conditional effect at\nlow personality-risk score", 
"center(drugcond)" = "Drug group's conditional effect at\nhigh personality-risk score") 
geniole$table3 %>% mutate(`Analysis and predictor of agression` = labels_recode) %>% 
  mutate_all(linebreak) %>%
  knitr::kable(digits = 3, booktabs = T, caption = "Reproduction of Table 3 (Geniole et al., 2019)", escape = F, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  pack_rows(group_label = "Analysis A", start_row = 1, end_row = 3) %>%
  pack_rows(group_label = "Analysis B", start_row = 4, end_row = 5)  #%>% landscape()
```

```{r genioletable4, echo=FALSE}
geniole$table4 %>% 
  mutate_all(linebreak) %>%
  knitr::kable(digits = 3, booktabs = T, caption = "Reproduction of Table 4 (Geniole et al., 2019)", escape = F, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  pack_rows(group_label = "Analysis A", start_row = 1, end_row = 7) %>%
  pack_rows(group_label = "Analysis B", start_row = 8, end_row = 9) %>%
  pack_rows(group_label = "Analysis C", start_row = 10, end_row = 13)  #%>% landscape()
```


```{r genioletable5, echo=FALSE}
geniole$table5 %>% 
#  mutate_all(linebreak) %>%
  knitr::kable(digits = 3, booktabs = T, caption = "Reproduction of Table 5 (Geniole et al., 2019)", escape = F, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
    pack_rows(group_label = "Analysis A", start_row = 1, end_row = 3) %>%
  pack_rows(group_label = "Analysis B", start_row = 4, end_row = 5) # %>% landscape()

```




# References {-}
